\chapter{Introduction}
This project deals with discovering hidden information in a large set of data using a graph representation. A short background to graph theory is given before the problem is discussed. Furthermore, this chapter describes the purpose and research question of this project along with limitations. 

\section{Background}
% What is the origin?
Graph theory has its origin in 1736 when Euler addressed the problem of crossing each of the seven bridges once and only once in the town of Köningsberg \cite{fouss2016algorithms}. The problem was solved by studying the topology of the town, representing the banks as nodes and bridges as edges, leading to the conclusion that it is not possible to travel each bridge and visit each bank once.

% What is the position of graph theory today?
Since Euler's discoveries, the interest for graph theory and network science has increased, not least since the emergence of social networking sites such as Facebook, Twitter and LinkedIn which has clearly boosted graph theory \cite{fouss2016algorithms,barabasi2016network}. Today the claim that networks are everywhere has become routine \cite{brandes2013} and network science has a natural presence in many different areas, including physics, economics, biology and psychology.

% Why is it interesting and what are the possibilities?
Network science aims at analyzing and extracting information from complex relational data, which using traditional join queries would have been difficult and time consuming. The network perspective allows us to address deep questions about complicated systems \cite{brandes2013}. According to \citet{robinson2013}, the real world is interrelated and diversified: uniform and rule-bound in some parts but exceptional and irregular in others, making network science a relevant tool.

For several decades, we have only explored a fraction of the potential in data, in many cases because of the available technologies forcing us to treat it as isolated islands of moderate significance \cite{robinson2013}. Graphs change this completely and let us extract more information than was previously possible.

% Previous studies on this subject
Graph data mining has been shown to be successful in different applications. \citet{bankFraud} show how fraud can be detected using a graph representations of data. Insurance fraud has been detected by identifying a pattern of relationships between different actors. This has also been performed in the context of bank fraud and e-commerce fraud with successful results. 

Using the concept of node similarity, \citet{Liben-Nowell2003} were able to predict missing links in a social network. Moreover, \citet{Zhou2009} used node similarity to predict missing links in six disparate networks, including an electric grid, internet, and a protein-protein network.

\citet{clauset2008Hierarchicalstructure} have studied networks and predicted missing links using the identification of hierarchical structures. They found good results for three disparate networks: a terrorist association network, a metabolic network of a bacteria, and a network of different grassland species. Their algorithm showed results far better than chance, making it possible to extract new fruitful information into the different domains. 

\section{Problem Discussion}
Recorded Future is a company that harvests data from the open, dark and deep web. They collect text fragments and perform natural language processing, extracting the essence of each text fragment, and save the information in a database. This information is then used for predictive purposes such as forecasting future cyber attacks.

The data is saved in a document database because of its extensive size. However, dealing with such databases often limits further analysis related to relations between objects. In order to enable relational analysis by graph theory, other design paradigms might be useful.

As one might imagine, the size of the Recorded Future database is huge. Although documents are a good way of storing big amounts of data, it is also limiting in the kind of analyses that can be performed. Today, many of Recorded Future's analyses are based on studying the relation between entities one step away from each other. Thus, one might wonder what information might be hidden in this massive amount of data.

Mining networks for relations can often lead to new insights \cite{hendrix2010}. However, problems associated with link analysis\footnote{Network science and link analysis relates to the same thing: analyzing and extracting relational information from complex data. Network science is the term originating from physics and is the term used across disciplines while link analysis has its origin in computer science. \cite{fouss2016algorithms}} include information overload, high search complexity, and heavy reliance on domain knowledge \cite{hendrix2010,schroeder2007}. Another aspect is the presence of uncertainties, noise or perturbations \cite{hendrix2010}. These are all important aspects that have to be taken into consideration when dealing with network science, making it far from trivial to practice. 

\section{Purpose and Research Questions}

The purpose of this study is to develop a strategy that enables relational analysis starting from a database of significant size. Furthermore, the purpose is to find cases and data sets where relational analysis can be applied and the methods can be validated. 

The purpose can be broken down into the following research questions
\begin{enumerate}
    \item What methodology and design is suitable for extracting hidden relations in a big database within reasonable execution time?
    \item What classes of network analysis is important when performing cyber threat analysis?
\end{enumerate}

\section{Delimitations}
\citet{brandes2013} are skeptical about a Grand Unified Network Theory since in their view, every network representation is related to its domain and the abstraction of the phenomenon that is of interest. And so, every graph is highly dependent on what domain it represents and what types of questions one is trying to answer \cite{hendrix2010, schroeder2007}. It is therefore important to point out that this project is limited to the data of Recorded Future and thus, the domain of cyber threat intelligence. 

This study is not exhaustive and will only deal with a portion of all the possible data sets that can be analyzed. Furthermore, the study only deals with a portion of the methods available and is therefore to be considered as a guide for future work that Recorded Future might perform.
